\section{球员}\label{224}

\subsection{违反体育精神的行为}\label{2241}

\begin{enumerate}[label=(\alph*)]
    \item \label{2241a}如果\\
    In the event of
    \begin{enumerate}[label=(\roman*)]
        \item 球员用冒犯性的话语，或做冒犯性的姿势；或\\
        a player using offensive language, or making offensive gestures; or
        \item 球员有任意行为，其在裁判看来是故意地或持续地违反体育精神的；或\\
        any conduct by a player which in the opinion of the referee is wilfully or persistently Unsporting; or
        \item 球员有任意其他行为，其另外累积到成为违背体育精神的行为；或\\
        any other conduct by a player which otherwise amounts to Unsporting Conduct; or
        \item 任意球员拒绝继续当局；\\
        any player refusing to continue the current frame;
    \end{enumerate}
    那么裁判应警告球员若再有任意违反体育精神的行为则此局会被判定他们的对方赢得。\\
    the referee shall Warn the player that in the event of any further Unsporting Conduct the frame will be awarded to their opponent.
    \item \label{2241b}如果裁判已根据上面\ref{2241a}警告过球员，那么若再有任意违反体育精神的行为，则裁判应判定此局他们的对方赢得，或者，若这发生在局间，则裁判应判定下一局他们的对方赢得，并且裁判应警告球员若再有任意违反体育精神的行为则此场会被判定他们的对方赢得。\\
    If the referee has Warned the player under \ref{2241a} above, in the event of any further Unsporting Conduct, the referee shall award the frame to their opponent, or, if this happens between frames, the referee shall award the next frame to their opponent, and the referee shall Warn the player that in the event of any further Unsporting Conduct the game will be awarded to their opponent.
    \item \label{2241c}如果裁判已根据上面\ref{2241b}或下面\ref{2241d}警告过球员，那么若所涉及的球员再有任意违反体育精神的行为，则裁判应判定此场此球员的对方赢得。\\
    If a referee has awarded a frame to a player's opponent, under \ref{2241b} above or \ref{2241d} below, in the event of any further Unsporting Conduct by the player concerned, the referee shall award the game to the player's opponent.
    \item \label{2241d}如果行为在裁判看来裁判是足够严重的，那么裁判应判此局或此场此球员的对方赢得，即使之前对违背体育精神的行为的警告未被宣布。\\
    In the event that the conduct, in the opinion of the referee is sufficiently serious, the referee shall award the frame or the game to the player's opponent, even if previous Warnings for Unsporting Conduct were not issued.
    \item 任何裁判的判定一局和/或场一位球员的对方赢得的决定都应是最终的且不应屈从于任何申诉。 \\
    Any decision by the referee to award a frame and/or game to a player's opponent shall be final and shall not be subject to any appeal.
\end{enumerate}

\subsection{认输}\label{2242}

\begin{enumerate}[label=(\alph*)]
    \item 球员可以提出认输，但如果他们的对手选择继续比赛那么其变得无效。\\
    A player may offer a concession, but this becomes null and void if their opponent chooses to play on.
    \item 球员不应在任何场或任何次比赛中认输一局除非任意球员需要罚分[才能获胜]。任何本规则的违反都应被视为所涉及的球员的违背体育精神的行为。如果裁判已根据上面规则\ref{2241}\ref{2241a}警告过球员，那么下一局应被判定他们的对方赢得。\\
    A player shall not concede a frame in any game, or match unless any player requires penalty points. Any breach of this Rule shall be regarded as Unsporting Conduct by the player concerned. If the referee has already Warned the player under Rule \ref{2241}\ref{2241a} above, the next frame shall be awarded to their opponent.
    \item \label{2242c}如果一位球员碰触或移动一颗或多颗球以指明提出认输，那么若认输被他们的对方接受则裁判不会宣告``犯规''或``受罚''。如果认输不被接受，那么第\ref{223}节规则\ref{22316}或第\ref{223}节规则\ref{2233k}应适用。\\
    If a player touches or moves a ball(s) in play to indicate the offering of a concession, the referee will not call FOUL or PENALTY if the concession is accepted by their opponent. If the concession is not accepted, Section \ref{223} Rule \ref{22316} or Section \ref{223} Rule \ref{2233k} shall apply.
    \item 如果一位球员在需要罚分才能赢得此局前故意造成违规从而由此他们现在需要罚分[才能赢得此局]，那么会被视为违反体育精神的行为并且此球员应被裁判如上面规则\ref{2241}\ref{2241a}和\ref{2241}\ref{2241b}中的警告。\\
    If a player, prior to needing penalty points to win the frame, intentionally commits an infringement so that, as a result, they now require penalty points, it will be deemed as Unsporting Conduct and the player shall be Warned by the referee as in Rule \ref{2241}\ref{2241a} or \ref{2241}\ref{2241b} above.
    \item 认输的提出或接受不能被撤回。\\
    The offer, or the acceptance of a concession, cannot be withdrawn.
    \item 当累计得分决定一场或一次比赛的胜者并且一局被认输时，对方应得到等价于台面上剩余的任何球的分数，此时红球应被每颗按八分算入并且任何错误地离开台面的彩球都应被按已摆上点位算入。\\
    When aggregate scores determine the winner of a game or a match and a frame is conceded, the opponent shall receive the equivalent of the value of any balls remaining on the table, where Reds shall count as eight points each and any colour incorrectly off the table shall be counted as if spotted.
\end{enumerate}

\subsection{浪费时间}\label{2243}

\begin{enumerate}[label=(\alph*)]
    \item \label{2243a}如果一位球员在击球或击球的选择中用异常量的时间，那么裁判应警告球员若再在比赛中浪费时间，则此局会被判定他们的对方赢得。\\
    In the event of a player taking an abnormal amount of time over a stroke, or the selection of a stroke, the referee shall Warn the player that in the event of any further Time Wasting during the game, the frame will be awarded to their opponent.
    \item \label{2243b}如果裁判已根据上面\ref{2243a}就浪费时间警告过球员，那么若此球员再浪费时间，则裁判应判定此局他们的对方赢得。\\
    If the referee has Warned the player for Time Wasting under \ref{2243a} above, in the event of any further Time Wasting by that player, the referee shall award the frame to their opponent.
    \item \label{2243c}如果裁判已就浪费时间判定一局一位球员的对方赢得，那么若所涉及的球员再浪费时间，则每再出现一次裁判都应判定一局此球员的对方赢得。\\
    If a referee has awarded a frame to a player's opponent for Time Wasting, in the event of any further Time Wasting by the player concerned, the referee shall, each time thereafter, award a frame to the player's opponent.
\end{enumerate}

\subsection{处罚细则}

\begin{enumerate}[label=(\alph*)]
    \item 如果一局根据本节被判定输掉，那么违规者应：\\
    If a frame is forfeited under this Section, the offender shall:
    \begin{enumerate}[label=(\roman*)]
        \item 输掉相关局；且\\
        lose the relevant frame; and
        \item 当累计得分决定一场或一次比赛的胜者时，失去所有得分并且对手应得到等价于台面上剩余的任何球的分数，此时红球应被每颗按八分算入并且任何错误地离开台面的彩球都应被按已摆上点位算入。\\
        when aggregate scores determine the winner of a game or match, forfeit all points scored and the opponent shall receive the equivalent of the value of any balls remaining on the table, where Reds shall count as eight points each and any colour incorrectly off the table shall be counted as if spotted.
    \end{enumerate}
    \item 如果一场根据本节被判定输掉，那么违规者应：\\
    If a game is forfeited under this Section, the offender shall:
    \begin{enumerate}[label=(\roman*)]
        \item 输掉相关局；并且\\
        lose the relevant frame; and
        \item 附带地，当局是[胜负]依据时输掉要求的或尚未进行的若干局以结束此场；或\\
        additionally, lose the required number of unplayed frames to complete the game where frames are relevant; or
        \item 附带地，当累计得分是[胜负]依据时，输掉剩下的局且每局值147分。\\
        additionally, lose the remaining frames, each valued at 147 points, where aggregate points determine the winner of the game.
    \end{enumerate}
\end{enumerate}

\subsection{非击球手}

\noindent 当击球手正在比赛时，非击球手应避免站在或移动于击球手的视线[范围]内。他们应坐下或站在与球台有合理距离处并避免任何可能影响击球手的注意力的移动或行为。\\
The non-striker shall, when the striker is playing, avoid standing or moving in the line of sight of the striker. They shall sit or stand at a reasonable distance from the table and avoid making any movement or action that may interrupt the concentration of the striker.

\subsection{计分的职责}

\noindent 同裁判一样，球员也有责任保证正确的得分被使用，不管是在记分牌上被使用还是被报得分的裁判使用。如果任意球员发现比分是不正确的，那么他们有责任尽早告诉裁判。\\
As well as the referee, it is the players' responsibility to make sure that the correct score is being applied, either on the scoreboard or by the referee announcing the scores. If any player notices that the score is incorrect, it is their responsibility to inform the referee at the earliest opportunity.

\subsection{离开场地}

\noindent 如果非击球手离开球桌，那么他们可以选定一位代表以照顾他们的利益并若有必要申明违规。这样的选定必须在离开前让裁判知晓。\\
In the case of their absence from the table, the non-striker may appoint a deputy to watch in their interest and claim an infringement if necessary. Such appointment must be made known to the referee prior to departure.
