\section{官员}\label{225}

\subsection{裁判}\label{2251}

\begin{enumerate}[label=(\alph*)]
    \item \label{2251a}裁判应：\\
    The referee shall:
    \begin{enumerate}[label=(\roman*)]
        \item \label{2251ai}对于任何本规则没有充分涵盖到的情况，根据公平竞赛原则做出决定；\\
        make decisions in the interests of fair play for any situation not covered adequately by these Rules;
        \item 根据本规则对一次比赛中的恰当行为负责\footnote{指让在场的所有人保持恰当行为。}；\\
        be responsible for proper conduct during a match under these Rules;
        \item 在看到任何本规则的违例时介入；\\
        intervene if they see any infringement of these Rules;
        \item 若被要求则告诉球员球的颜色或其位置；并\\
        tell a player the colour of a ball, or its position, if requested; and
        \item 根据击球手的合理要求清洁比赛用球。\\
        clean any ball upon reasonable request by the striker.
    \end{enumerate}
    \item 裁判不应：\\
    The referee shall not:
    \begin{enumerate}[label=(\roman*)]
        \item 回答任何本规则中未授权[可以回答]的问题；或\\
        answer any question not authorised in these Rules; nor
        \item 当球员将要造成违规时给予任何暗示；或\\
        give any indication that a player is about to commit an infringement; nor
        \item 对可能影响比赛的情况给予任何建议或意见；或\\
        give any advice or opinion on situations that could affect play; nor
        \item 回答任何关于得分差的问题。\\
        answer any question regarding the difference in scores.
    \end{enumerate}
    \item 如果裁判未能注意到突发情况，那么他们可以根据他们的判断听取在最佳观察位置的记分员或其他官员或观众的证言或者如果可行他们可以观看记录突发情况的照相机/录像机来协助他们的决定。\\
    If the referee has failed to notice any incident, they may at their discretion take the evidence of the marker or other officials or spectators best placed for the observation or, if available, they may view a camera/video recording of the incident to assist their decision.
\end{enumerate}

\subsection{记分员}

\noindent 记分员应维护记分牌上的得分并协助裁判履行他们的职责。记分员若有必要也应担任记录员。\\
The marker shall keep the score on the scoreboard and assist the referee in carrying out their duties. The marker shall also act as a stroke recorder if necessary.

\subsection{记录员}

\noindent 记录员应按要求做每一次击打或违规，和每位球员或每一
方得多少分的记录。他们也应做单杆总分和宣布的警告的记录。\\
The stroke recorder shall maintain a record of each stroke or infringement and how many points are scored by each player or side as required. They shall also make a note of break totals and Warnings where issued.

\subsection{来自官员的协助}

\begin{enumerate}[label=(\alph*)]
    \item 应击球手的要求，裁判或记分员应移动并暂持影响到进行一次击球中的击球手的行为的任何照明设备。\\
    At the striker's request, the referee or marker shall move and hold in position any lighting apparatus that interferes with the action of the striker in making a stroke.
    \item 根据残障球员的具体情况，裁判员或记分员可以给予他们必要的协助。\\
    It is permissible for the referee or marker to give necessary assistance to players with disabilities according to their circumstances.
\end{enumerate}
